\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-01 paper.qmd
Add simulate data description

The S-curve model, denoted as $T$, is simulated through several steps. First, a random variable $x$ is generated from a uniform distribution between $-\frac{\pi}{2}$ and $\frac{\pi}{2}$, representing the parameter $a$ in the S-curve model. Next, three variables $x_1$, $x_2$, and $x_3$ are computed based on $x$ to construct the S-curve data. $x_1$ is calculated as the sine of $a$ (@eq-eqn1), $x_2$ as twice the value of another uniformly distributed random variable between 0 and 1 (@eq-eqn2), and $x_3$ as the cosine of $a$ minus 1, multiplied by the sign of $a$ (@eq-eqn3). Additionally, four noise dimensions are introduced to the dataset to introduce variability: $x_4$, $x_5$, $x_6$, and $x_7$, each generated from uniform distributions within specific intervals (@eq-eqn4, @eq-eqn5, and @eq-eqn6 respectively). Finally, these variables are combined to form the S-curve dataset $T$.

$$
x_1 = \sin(3 \pi x)
$$ {#eq-eqn1}

@@

$$
x_3 = \text{sign}(x) \times (\cos(3 \pi x) - 1)
$$ {#eq-eqn3}

>>>>

First, a random variable $a$ is generated from a uniform distribution between $-\frac{\pi}{2}$ and $\frac{\pi}{2}$, representing the parameter $a$ is in $T$. Next, three variables $x_1$, $x_2$, and $x_3$ are computed based on $a$ to construct the S-curve data. $x_1$ is calculated as the sine of $a$ (@eq-eqn1), $x_2$ as twice the value of another uniformly distributed random variable between 0 and 1 (@eq-eqn2), and $x_3$ as the cosine of $a$ minus 1, multiplied by the sign of $a$ (@eq-eqn3). Additionally, four noise dimensions are introduced to the dataset to introduce noise variability: $x_4$, $x_5$, $x_6$, and $x_7$, each generated from uniform distributions within specific intervals (@eq-eqn4, @eq-eqn5, and @eq-eqn6 respectively). Finally, these variables are combined to form the S-curve dataset $T$.

$$
x_1 = \sin(3 \pi a)
$$ {#eq-eqn1}

@@

$$
x_3 = \text{sign}(a) \times (\cos(3 \pi a) - 1)
$$ {#eq-eqn3}

### 2024-04-01 paper.tex
Add simulate data description

The S-curve model, denoted as \(T\), is simulated through several steps.
First, a random variable \(x\) is generated from a uniform distribution
between \(-\frac{\pi}{2}\) and \(\frac{\pi}{2}\), representing the
parameter \(a\) in the S-curve model. Next, three variables \(x_1\),
\(x_2\), and \(x_3\) are computed based on \(x\) to construct the
S-curve data. \(x_1\) is calculated as the sine of \(a\)
(Equation~\ref{eq-eqn1}), \(x_2\) as twice the value of another
uniformly distributed random variable between 0 and 1
(Equation~\ref{eq-eqn2}), and \(x_3\) as the cosine of \(a\) minus 1,
multiplied by the sign of \(a\) (Equation~\ref{eq-eqn3}). Additionally,
four noise dimensions are introduced to the dataset to introduce
variability: \(x_4\), \(x_5\), \(x_6\), and \(x_7\), each generated from
uniform distributions within specific intervals (Equation~\ref{eq-eqn4},
Equation~\ref{eq-eqn5}, and Equation~\ref{eq-eqn6} respectively).
Finally, these variables are combined to form the S-curve dataset \(T\).

\begin{equation}\phantomsection\label{eq-eqn1}{
x_1 = \sin(3 \pi x)
}\end{equation}

@@

\begin{equation}\phantomsection\label{eq-eqn3}{
x_3 = \text{sign}(x) \times (\cos(3 \pi x) - 1)
}\end{equation}

>>>>

First, a random variable \(a\) is generated from a uniform distribution
between \(-\frac{\pi}{2}\) and \(\frac{\pi}{2}\), representing the
parameter \(a\) is in \(T\). Next, three variables \(x_1\), \(x_2\), and
\(x_3\) are computed based on \(a\) to construct the S-curve data.
\(x_1\) is calculated as the sine of \(a\) (Equation~\ref{eq-eqn1}),
\(x_2\) as twice the value of another uniformly distributed random
variable between 0 and 1 (Equation~\ref{eq-eqn2}), and \(x_3\) as the
cosine of \(a\) minus 1, multiplied by the sign of \(a\)
(Equation~\ref{eq-eqn3}). Additionally, four noise dimensions are
introduced to the dataset to introduce noise variability: \(x_4\),
\(x_5\), \(x_6\), and \(x_7\), each generated from uniform distributions
within specific intervals (Equation~\ref{eq-eqn4},
Equation~\ref{eq-eqn5}, and Equation~\ref{eq-eqn6} respectively).
Finally, these variables are combined to form the S-curve dataset \(T\).

\begin{equation}\phantomsection\label{eq-eqn1}{
x_1 = \sin(3 \pi a)
}\end{equation}

@@

\begin{equation}\phantomsection\label{eq-eqn3}{
x_3 = \text{sign}(a) \times (\cos(3 \pi a) - 1)
}\end{equation}
